# Studies considered in meta-analysis

* 2001  
   + Bongeen #1  
   + Bongeen #2  
   
* 2002
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy
   
* 2004
   + Redvale

* 2010  
   + Hermitage  
   + Kingaroy  
   
* 2011  
   + Hermitage  
   + Kingaroy  
   
* 2012  
   + Gatton  
   + Kingaroy  
   
* 2013
   + Premer; no raw data
   + Milmerran; no raw data
   + Mt Mary; no raw data
   + Goolhi; no raw data

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due it insuficient/late disease infection  
   + Emerald  
   
* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald
   
* 2017  
   + Fogerty  
   + Hermitage  

* 2018
   + Wellcamp
   
* 2019
   + Hermitage


**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery Mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
Comparing Trials which have not used the same rating scale wil be done using a percentage change.  



**2013 Field trials**  
Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.  

```{r}
knitr::kable(
   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
         Active_Ingredient = c("Sulphur", "Propiconazole", "Amistar", "Carbendazim")
   )
)
```

## Experimental locations
```{r Experiment_locations}

experiment_sites <- data.frame(
   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
   lat = c(-28.215 ,-26.58,-27.56,-23.54),
   lon = c(152.1003,151.83,152.32,148.19)
)



 leaflet() %>%
    addProviderTiles("Esri.WorldTopoMap") %>%
    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)


```

