# Studies considered in meta-analysis

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
library(dplyr)
library(readr)
library(kableExtra)
library(leaflet)
library(htmltools)
source("R/import_data.R")
```

* 2001  
   + Bongeen #1  
   + Bongeen #2  
   
* 2002  
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy  
   
* 2004  
   + Redvale  

* 2010  
   + Hermitage  
   + Kingaroy  
   
* 2011  
   + Hermitage  
   + Kingaroy  
   
* 2012  
   + Gatton  
   + Kingaroy  
   
* 2013  
   + Premer  
   + Milmerran   
   + Mt Mary   
   + Goolhi  

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due to insufficient/late disease infection  
   + Emerald  
   
* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald  
   
* 2017  
   + Missen Flats (Fogerty's farm)  
   + Hermitage  

* 2018  
   + Wellcamp  
   
* 2019  
   + Hermitage  


**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
Comparing trials which have not used the same rating scale will be done using a percentage change.  

**2013 Field trials**  
Trials were conducted by the National Growers Alliance (NGA). The raw data were obtained from Lawrie Price. NGA data were formatted to be compliant with existing data rating and scales in the R script `Cleaning historical data.R`.

## Summary of data  

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

# source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports

PM.dat <- import_data()


glimpse(PM.dat)

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(n_treatment)),
   caption = "Description of Experiments"
 ) # %>%  #commented as was redering empty, needs a look in
#    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
#    scroll_box(width = "900px", height = "500px")

```

## Experimental locations

Experimental locations where data was sufficient to include in meta-analysis.

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
      ),
   lat = c(-28.215 , -26.58, -27.56, -23.54, -27.51666, -31.43449, -27.923674, -31.0142, -31.00246, -27.905313, -27.564277),
   lon = c(152.1003, 151.83, 152.32, 148.19, 151.450,150.0052, 151.242706, 150.05018, 149.82507, 151.9772,151.867879)
)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
#   addPopups(lng = experiment_sites$lon, lat = experiment_sites$lat, popup = experiment_sites$location)

```

