# Studies considered in meta-analysis

```{r MEsummary_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(leaflet)
#source("./getPPD2.R")

```

* 2001  
   + Bongeen #1  
   + Bongeen #2  
   
* 2002
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy
   
* 2004
   + Redvale

* 2010  
   + Hermitage  
   + Kingaroy  
   
* 2011  
   + Hermitage  
   + Kingaroy  
   
* 2012  
   + Gatton  
   + Kingaroy  
   
* 2013
   + Premer; no raw data
   + Milmerran; no raw data
   + Mt Mary; no raw data
   + Goolhi; no raw data

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due it insuficient/late disease infection  
   + Emerald  
   
* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald
   
* 2017  
   + Fogerty  
   + Hermitage  

* 2018
   + Wellcamp
   
* 2019
   + Hermitage


**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery Mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
Comparing Trials which have not used the same rating scale wil be done using a percentage change.  



**2013 Field trials**  
Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.  

```{r}
knitr::kable(
   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
         Active_Ingredient = c("Sulphur", "Propiconazole", "Amistar", "Carbendazim")
   )
)
```

## Summary of data  

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports


PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

glimpse(PM.dat)


kable(PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   scroll_box(width = "900px", height = "500px")



PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)


```



## Experimental locations
Experimental locations where data was sufficient to include in meta-analysis
```{r Experiment_locations}

experiment_sites <- data.frame(
   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
   lat = c(-28.215 ,-26.58,-27.56,-23.54),
   lon = c(152.1003,151.83,152.32,148.19)
)



 leaflet() %>%
    addProviderTiles("Esri.WorldTopoMap") %>%
    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)


```

