# Studies considered in meta-analysis

This meta-analysis uses data collected by a number of researchers from the
Department of Agriculture and Primary Industries and the University of Southern
Queensland. It is worth noting Professor Malcolm Riley's and Dr Sue Thompson's
effort in establishing and coordinating early field trials between 2010 and
2016.

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, leaflet, htmltools)
source("R/import_data.R")
```

* 2001  
   + Bongeen #1  
   + Bongeen #2  
   
* 2002  
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy  
   
* 2004  
   + Redvale  

* 2010  
   + Hermitage  
   + Kingaroy  
   
* 2011  
   + Hermitage  
   + Kingaroy  
   
* 2012  
   + Gatton  
   + Kingaroy  
   
* 2013  
   + Premer  
   + Millmerran   
   + Marys Mount  
   + Goolhi  

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due to insufficient/late disease infection  
   + Emerald  
   
* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald  
   
* 2017  
   + Missen Flats (Fogerty's farm)  
   + Hermitage  

* 2018  
   + Wellcamp  
   
* 2019  
   + Hermitage  


**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
file "Powdery mildew paper#1.doc".  
Comparing trials which have not used the same rating scale will be done using a
percentage change.  

**2013 Field trials**  
Trials were conducted by the National Growers Alliance (NGA). The raw data were
obtained from Lawrie Price. NGA data were formatted to be compliant with
existing data rating and scales in the R script `Cleaning historical data.R`.  

## Summary of data  

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
PM.dat <- import_data()

kable(
   PM.dat %>%
      group_by(
         trial_ref,
      ) %>%
      summarise(year = unique(year),
                location = unique(location),
                mean_treat_replicates = mean(replicates),
                planting_date = unique(planting_date),
                first_sign_disease = unique(first_sign_disease),
                treatments = length(n_treatment)),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```

## Powdery mildew ratings  

   1. No powdery mildew colonies observed on any plant  
   2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected  
   3. Colonies in lower 1/2 of canopy, >75% of plants affected  
   4. Colonies in lower 2/3 of canopy, up to 75% of plants affected  
   5. Colonies in lower 2/3 of canopy, >75% of plants affected  
   6. Colonies in lower 2/3 of canopy, 100% of plants affected  
   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy  
   8. Colonies to top of plant with >75% of plants affected  
   9. Colonies to top of plant with 100% of plants affected and heavy leaf drop  


## Experimental locations  

Experimental locations where data was sufficient to include in meta-analysis.  

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
   ),
   lat = c(
      -28.215 ,
      -26.58,
      -27.56,
      -23.54,
      -27.51666,
      -31.43449,
      -27.923674,
      -31.0142,
      -31.00246,
      -27.905313,
      -27.564277
   ),
   lon = c(
      152.1003,
      151.83,
      152.32,
      148.19,
      151.450,
      150.0052,
      151.242706,
      150.05018,
      149.82507,
      151.9772,
      151.867879
   )
)

write.csv(experiment_sites,
          "cache/Mungbean_experiment_sites.csv",
          row.names = FALSE)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31,
           lng = 150.456,
           zoom = 5) %>%
   addMarkers(
      lng = ~ lon,
      lat = ~ lat,
      popup = ~ htmlEscape(location)
   )
```
