# Studies considered in meta-analysis

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
library(dplyr)
library(readr)
library(kableExtra)
library(leaflet)
source("R/import_data.R")
```

* 2001  
   + Bongeen #1  
   + Bongeen #2  
   
* 2002
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy
   
* 2004
   + Redvale

* 2010  
   + Hermitage  
   + Kingaroy  
   
* 2011  
   + Hermitage  
   + Kingaroy  
   
* 2012  
   + Gatton  
   + Kingaroy  
   
* 2013
   + Premer; no raw data
   + Milmerran; no raw data
   + Mt Mary; no raw data
   + Goolhi; no raw data

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due to insufficient/late disease infection  
   + Emerald  
   
* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald
   
* 2017  
   + Missen Flats (Fogerty's farm)  
   + Hermitage  

* 2018
   + Wellcamp
   
* 2019
   + Hermitage


**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript. 
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc". 
Comparing trials which have not used the same rating scale will be done using a percentage change. 

**2013 Field trials**  
Fungicide treatments were described in reports in two letter acronyms.
The following is the assumed usage.  

```{r}
knitr::kable(cbind(
   Acronym = c("SF", "Ti", "AX", "Ca"),
   `Expected Fungicide` = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
   `Active Ingredient` = c(
      "Sulphur",
      "Propiconazole",
      "Azoxystrobin and Cyproconazole",
      "Carbendazim"
   )
))
```

## Summary of data  

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

# source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports

PM.dat <- import_data()

glimpse(PM.dat)

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(e_treatment)),
   caption = "Description of Experiments"
) %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")

```

## Experimental locations

Experimental locations where data was sufficient to include in meta-analysis.

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College"
   ),
   lat = c(-28.215 , -26.58, -27.56, -23.54),
   lon = c(152.1003, 151.83, 152.32, 148.19)
)

leaflet() %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)
```

